Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Enhanced Flexibility

### 2025-02-13 review/response_241203.tex

\input{../manuscript/preamble}
\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-32387-2024}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of T-SP-32387-2024.
	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest version for your convenience.
	The title has been changed to \emph{MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS} to better reflect the content of the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{editor}
	\summary{
		The reviewers raised a number of concerns regarding the paper's contribution, novelty, and mathematical correctness, which led to the recommendation for rejection. The main issues identified include:
		\begin{enumerate}
			\item The contribution of the paper is unclear. Specifically, the proposed framework in \eqref{op:shaping} is not sufficiently general as it does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality). A more general case has already been investigated and solved in the authors' previous work \cite{Zhou2023}. Some content in Section \ref{sc:shaping_numerical} are well established methods in the literature \cite{Abrudan2008}. \label{sm:a}
			\item The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty. The reviewer pointed that they can be possibly solved by existing methods through appropriate adjustment \cite{Santamaria2023,Li2023b}. Also, it is also pointed out that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are the standard results from matrix textbook. \label{sm:b}
			\item The correctness and usefulness of the mathematical derivations. For example, the derivation in the proof of Appendix \ref{ap:shaping} is incorrect. Convergence proof in Appendix \ref{ap:power} is questionable. The usefulness of these bounds on singular values of the effective channel $\mathbf{H}$ is unclear. \label{sm:c}
			\item The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed. \label{sm:d}
			\item The simulation study can be enhanced. For example, comparisons with the \gls{d}-\gls{ris} and a globally passive \gls{bd}-\gls{ris} were suggested by the reviewer. \label{sm:e}
		\end{enumerate}
	}

	\reply{
		We appreciate the editor's summary of the comments. We have carefully considered each point raised and have made significant revisions to address these concerns. Please refer to \ref{cm:a} for \ref{sm:a}, \ref{cm:b1} and \ref{cm:b2} for \ref{sm:b}, \ref{cm:c1} and \ref{cm:c2} and \ref{cm:b2} for \ref{sm:c}, \ref{cm:b1} for \ref{sm:d}, and \ref{cm:e} for \ref{sm:e} in the following responses.
	}

@@

\end{editor}

\begin{reviewer}
	\summary{
		This manuscript investigates the impact of \gls{bd}-\gls{ris} to the distribution of singular values of \gls{mimo} channel of a point-to-point communication system. Especially, the authors derive bounds of singular values of \gls{bd}-\gls{ris} channel and propose algorithms to design \gls{bd}-\gls{ris} configuration.
	}

	\comment{
		\label{cm:a}
		The contribution of Sec. \ref{sc:shaping_numerical} is unclear for the following two reasons.
		\begin{enumerate}
			\item The manuscript claims to propose a universal optimization framework for \gls{bd}-\gls{ris} as in \eqref{op:shaping}. However, the framework in \eqref{op:shaping} is indeed not sufficiently general. It does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality) besides the orthogonal conditions \eqref{cn:shaping_unitary}. The reviewer notice that a more general framework, which considers \gls{bd}-\gls{ris} constraints in addition to \eqref{cn:shaping_unitary}, has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
			\item Besides, both the non-geodesic \gls{rcg} and geodesic \gls{rcg} algorithms, e.g., \eqref{eq:gradient_eucl} -- \eqref{eq:geodesic_tran}, are well established methods in the literature, e.g., \cite{Abrudan2008}. Therefore, the novelty of Sec. \ref{sc:shaping_numerical} unclear.
		\end{enumerate}
	}

	\reply{
		We appreciate the reviewer's insightful comments.
		The geodesic \gls{rcg} algorithm for unitary-constrained problems has indeed been proposed in the optimization literature.
		Our contribution is an extension to block-unitary cases with parallel or unified updates that accelerate the design of group-connected \gls{bd}-\gls{ris}.
		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been remove and we have completely reworked the optimization part to reflect the particular contributions (channel shaping).
		The content is too long to fit here and we kindly ask the reviewer to refer to Section \ref{sc:shaping_numerical} of the revised manuscript for details.
	}

@@

	\comment{
		In Sec. \ref{sc:shaping_numerical}, the manuscript proposes to maximize weighted sum of singular values of the effective channel $\mathbf{H}$. The optimization objective is rather vague. Is the weighted sum of singular values related to any meaningful performance metric (e.g., capacity, power gain, and so on)?
	}

	\reply{
		This is an important question.
		The weighted sum of singular values plays a crucial role in channel shaping since it helps to reveal the achievable singular value region.
		We believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris}.
		We have added a detailed explanation in the revised manuscript and the answer comprises two parts below.

		\change{
			To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
			\begin{maxi*}
				{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{}{}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
			\end{maxi*}
			where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
			Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
			While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication, detection probability for sensing, and harvestable energy for power transfer).
			Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
			It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
		}

		\change{
			\setcounter{figure}{1}
			\begin{figure}[H]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)]{
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}
				\subfloat[$2 \times 32 \times 2$]{
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32.tex}
				\\
				\subfloat[$2 \times 64 \times 2$]{
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx64.tex}
				\subfloat[$2 \times 128 \times 2$]{
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx128.tex}
				\caption{Achievable singular value regions of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel shaped by \gls{bd}-\gls{ris}. The singular value pair of the direct channel are marked as baseline.
				On the Pareto frontiers, `P-max', `E-max', and `R-max' refer to the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc, respectively.}
			\end{figure}
			Fig. \ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as derived in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
			This observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$.
			Fig. \subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
			It verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
			As a consequence, \emph{the optimally shaped channels for different applications coincide with each other,} which emphasizes the benefits of \emph{multi-functional} \gls{bd}-\gls{ris}.
			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one, which can be leveraged for interference mitigation and secure communication.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.

	\comment{
		\label{cm:c1}
		Derivation in the proof of Appendix \ref{ap:shaping} is incorrect. Specifically, $(\partial \mathbf{u}^\mathsf{T}) \cdot \mathbf{u}$ is not equal to $\partial (\mathbf{u}^T \mathbf{u})$. Similar error occurs to $\mathbf{v}$. Please note that the derivative of singular value of a matrix with respect to the matrix itself does not exist. In fact, sub-differential should be used instead, e.g., \cite{Cai2010}.
	}

	\reply{
		We appreciate the reviewer for pointing out the error.
		We have corrected the derivation in the proof of Appendix \ref{ap:shaping} and have used the sub-differential to handle the non-differentiability of the singular value function.
		\change{
			Consider a special class of channel shaping problem
			\begin{maxi*}
				{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{}{}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
			\end{maxi*}
			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
			Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
			Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
			\setcounter{proposition}{3}
			\begin{proposition}
				The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
				\begin{equation*}
					\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
				\end{equation*}
				where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
			\end{proposition}
		}
	}

	\comment{
		\label{cm:c2}
		The rank equation in the proof of Prop. \ref{pp:dof} (Appendix \ref{ap:dof}) seems confusing. The rank of product of two matrices is: $\rank(\mathbf{AB}) = \rank(\mathbf{B}) - \dim(\ker(\mathbf{A}) \cap \ran(\mathbf{B}))$. How could one obtain the rank equation in Appendix \ref{ap:dof}? Please clarify.
	}

	\reply{
		Using the rank equation pointed out by the reviewer, we realized that the achievability proof was incorrect, and the proposition itself was incorrect.
		We really appreciate the reviewer for pointing out this mistake!
		A new proof in Appendix \ref{ap:dof} shows that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
		The change in the main text is as follows.
		\change{
			\setcounter{proposition}{0}
			\begin{proposition}[Degrees of freedom]
				\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnotetext{Here communication \gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}. The concept is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
			\end{proposition}
			\begin{proof}
				Please refer to Appendix~\ref{ap:dof}.
			\end{proof}

			While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the ability to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
			% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
			% , it does not necessarily imply a higher rate at finite \gls{snr}.
			% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.

### 2025-02-13 assets/poster/power_sx_txrx16.tex
:construction: Fix plot legend

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.71952537202106e-05,
ymax=0.000358145391898644,
yminorticks=true,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
font=\tiny,
title style={font=\tiny},
label style={font=\tiny},
ticklabel style={font=\tiny},
legend style={font=\tiny},
x label style={yshift=10pt},
y label style={yshift=-7pt}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.12581618107481e-05\\
2	8.12581618107481e-05\\
3	8.12581618107481e-05\\
4	8.12581618107481e-05\\
5	8.12581618107481e-05\\
6	8.12581618107481e-05\\
7	8.12581618107481e-05\\
8	8.12581618107481e-05\\
9	8.12581618107481e-05\\
};
\addlegendentry{No RIS}

>>>>

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.71952537202106e-05,
ymax=0.000358145391898644,
yminorticks=true,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
x label style={yshift=10pt},
y label style={yshift=-7pt}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.12581618107481e-05\\
2	8.12581618107481e-05\\
3	8.12581618107481e-05\\
4	8.12581618107481e-05\\
5	8.12581618107481e-05\\
6	8.12581618107481e-05\\
7	8.12581618107481e-05\\
8	8.12581618107481e-05\\
9	8.12581618107481e-05\\
};
\addlegendentry{No RIS}

### 2025-02-13 assets/poster/singular_bound_rank2_sx128.tex
:construction: Fix plot legend

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.004,
% ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
0.8375	0.00142543267002251\\
1.8375	0.000656306214245826\\
2.8375	0.000132970460937413\\
3.8375	3.2994096547908e-20\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.000316188517375316\\
1.8375	0.000636356951614819\\
2.8375	0.000675093172956787\\
3.8375	0.000311028141103694\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

>>>>

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.004,
% ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}},
y label style={yshift=-7pt}
]
\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
0.8375	0.00142543267002251\\
1.8375	0.000656306214245826\\
2.8375	0.000132970460937413\\
3.8375	3.2994096547908e-20\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.000316188517375316\\
1.8375	0.000636356951614819\\
2.8375	0.000675093172956787\\
3.8375	0.000311028141103694\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

### 2025-02-13 assets/simulation/pc_power_sx_txrx16.tex
:construction: Fix plot legend

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.71952537202106e-05,
ymax=0.000358145391898644,
yminorticks=true,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.12581618107481e-05\\
2	8.12581618107481e-05\\
3	8.12581618107481e-05\\
4	8.12581618107481e-05\\
5	8.12581618107481e-05\\
6	8.12581618107481e-05\\
7	8.12581618107481e-05\\
8	8.12581618107481e-05\\
9	8.12581618107481e-05\\
};
\addlegendentry{No RIS}

>>>>

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.71952537202106e-05,
ymax=0.000358145391898644,
yminorticks=true,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.12581618107481e-05\\
2	8.12581618107481e-05\\
3	8.12581618107481e-05\\
4	8.12581618107481e-05\\
5	8.12581618107481e-05\\
6	8.12581618107481e-05\\
7	8.12581618107481e-05\\
8	8.12581618107481e-05\\
9	8.12581618107481e-05\\
};
\addlegendentry{No RIS}

### 2025-02-13 assets/simulation/pc_power_sx_txrx16_nd.tex
:construction: Fix plot legend

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymin=0,
ymax=0.000116439758271769,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.18421179472296e-07\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor4, forget plot] table[row sep=crcr]{%
x	y\\
6	2.47795062804422e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor6, forget plot] table[row sep=crcr]{%
x	y\\
7	8.20088397806638e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
8	2.94451091720999e-05\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor10, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000111552731718914\\
};
\addplot[draw=none, only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor12] table[row sep=crcr]{%
x	y\\
0	0\\
};
\addlegendentry{Explicit}

>>>>

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymin=0,
ymax=0.000116439758271769,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.18421179472296e-07\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor4, forget plot] table[row sep=crcr]{%
x	y\\
6	2.47795062804422e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor6, forget plot] table[row sep=crcr]{%
x	y\\
7	8.20088397806638e-06\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
8	2.94451091720999e-05\\
};
\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor10, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000111552731718914\\
};
\addplot[draw=none, only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor12] table[row sep=crcr]{%
x	y\\
0	0\\
};
\addlegendentry{Explicit}
